### 2021-04-13 paper.Rmd
figure references made consistent

\begin{figure*}
   \centering
         \includegraphics[width=\textwidth]{figures/notation-huber.pdf}
\caption{Huber's plot (left) of the penguins data (bill length and depth only). The solid ellipse represents how well the projection, onto different directions, separates the three species and the dashed circle is a reference guide. The histogram (right) is the 1D projection of the data onto the direction outlined as the solid line in the huber's plot. Adapted from E.-K. Lee et al. (2005), Figure 1. }
\label{fig:notation-huber}
\end{figure*}

@@

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.2\textwidth]{figures/roman-surface-centered-010.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/torus-4-centered-015.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/cube-6-centered-001.png}}
\centerline{
\includegraphics[width=0.2\textwidth]{figures/roman-surface-centered-032.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/torus-4-centered-033.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/cube-6-centered-063.png}
}
\caption{Still views of the slice tour display showing geometric shapes: Roman surface (left), 4D torus (middle) and a 6d cube (right). Adapted from Laa, Cook and Valencia (2020), Fig. 4.}
\label{fig:tour-slice}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/pollen_sage-088.png}
\includegraphics[width=0.3\textwidth]{figures/pollen_sage_R1-088.png}
\includegraphics[width=0.3\textwidth]{figures/pollen_sage_gam20-088.png}
\caption{Snapshots of the same projection from the sage tour on the pollen data, illustrating the different tuning options. Left: using the default settings for the transformation results in a similar view as found in projections without the sage transformation. Middle: using the tuning parameter $R$ for better resolution near the center reveals the word "EUREKA". Right: using the $\gamma$ tuning parameter can also reveal the structure. Adapted from Laa, Cook and Lee, Fig. 9.}
\label{fig:pollen}
\end{figure}

@@

\begin{figure*}
   \centering
         \includegraphics[width=0.9\textwidth]{figures/liminal-stop-pause-refresh.png}
\caption{The clustering example from Figure \ref{fig:tsne-tour} using the liminal interface. Here a grand tour is displayed on the right hand side, with buttons allowing users to play, pause and refresh the tour animation. Adapted from Lee, Laa and Cook, 2020 Figure 2.}
\label{fig:tour-controls}
\end{figure*}

@@

\begin{figure}[htp]
\centerline{{\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp1.pdf}}
 {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp2.pdf}}
 {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp5.pdf}}}
\smallskip
\centerline{{\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp7.pdf}}
 {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp8.pdf}}
 {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp9.pdf}}}
\centerline{{\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp10.pdf}}
  {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp11.pdf}}
  {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp13.pdf}}}
\caption{Stepwise identification of clusters in the physics data. Each time a cluster is clearely separated we stop the tour and brush the points, followed by another spin of the data, until we can capture the full distribution. Adapted from Cook and Swayne, 2007 Figure 5.3.}
\label{fig:prim7-tour}
\end{figure}

@@

\begin{figure*}
  \centering
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-orange.png}
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-green.png}
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-purple.png}
  \caption{A grand tour run on the prediction boundaries of a radial support vector machine. (Left) The prediction region for points classified as orange produces a slice of a cube. (Middle) The predicition region for points classified as green produces another slice of the cube. (Right) The complete prediction region shows the points classified as purple are embedded within the green slice. Adapted from Wickham, Hoffman and Cook, 2015.}
  \label{fig:svm-tour}
\end{figure*}

@@

\begin{figure*}
   \centering
         \includegraphics[width=0.9\textwidth]{figures/scheidigger_nn_tour.png}
\caption{A grand tour run on the output of a deep neural network model for classification. The axes correspond to the probabilities that the model of an image belonging to a certain class. Adapted from Li, Zhao and Scheidigger, 2020.}
\label{fig:tour-nn}
\end{figure*}

@@

\begin{figure*}
  \centering
           \includegraphics[width=0.45\textwidth]{figures/allcenter-301.png}
         \includegraphics[width=0.45\textwidth]{figures/jetCluster-027.png}
\caption{Selected frames from using a grand tour of the physics data. Left: the three different types of measurements (shown in different colors) are aligned along different directions in parameter space. Right: an outlying point is marked with an asterisk symbol in the ATLAS7new facet. Adapted from Cook, Laa and Valencia, 2018, Figures 6 and 7.}
\label{fig:physics}
\end{figure*}

@@

\caption{Selected frames from using a grand tour of mouse retina single cell RNA-seq data with the radial transformation. The sage display was used to identify and verify cluster sepearation between the three highlighted clusters estimated from a clustering algorithm. Adapted from Laa, Lee and Cook, 2020 Figure 6.}
\label{fig:mouse-cluster}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.24\textwidth]{figures/torus-rings-4-with-torus-1.pdf}\includegraphics[width=0.24\textwidth]{figures/torus-rings-4-with-torus-2.pdf}
  \includegraphics[width=0.24\textwidth]{figures/torus-flat-6-1.pdf}\includegraphics[width=0.24\textwidth]{figures/torus-flat-6-2.pdf}
\caption{Several views of torii: (two at left) 4D ring torus, and (two at right) 6D flat torus. In each case, a subset has been highlighted which illustrate the low-dimensional donut shapes.}
\label{fig:geozoo}
\end{figure*}

>>>>

\begin{figure*}
   \centering
         \includegraphics[width=\textwidth]{figures/notation-huber.pdf}
\caption{Huber's plot (left) of the penguins data (bill length and depth only). The solid ellipse represents how well the projection, onto different directions, separates the three species and the dashed circle is a reference guide. The histogram (right) is the 1D projection of the data onto the direction outlined as the solid line in the huber's plot. (Adapted from E.-K. Lee et al. 2005, Figure 1.) }
\label{fig:notation-huber}
\end{figure*}

@@

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.2\textwidth]{figures/roman-surface-centered-010.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/torus-4-centered-015.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/cube-6-centered-001.png}}
\centerline{
\includegraphics[width=0.2\textwidth]{figures/roman-surface-centered-032.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/torus-4-centered-033.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/cube-6-centered-063.png}
}
\caption{Still views of the slice tour display showing geometric shapes: Roman surface (left), 4D torus (middle) and a 6d cube (right). (Adapted from Laa, Cook and Valencia, 2020, Figure 4.)}
\label{fig:tour-slice}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/pollen_sage-088.png}
\includegraphics[width=0.3\textwidth]{figures/pollen_sage_R1-088.png}
\includegraphics[width=0.3\textwidth]{figures/pollen_sage_gam20-088.png}
\caption{Snapshots of the same projection from the sage tour on the pollen data, illustrating the different tuning options. Left: using the default settings for the transformation results in a similar view as found in projections without the sage transformation. Middle: using the tuning parameter $R$ for better resolution near the center reveals the word "EUREKA". Right: using the $\gamma$ tuning parameter can also reveal the structure. (Adapted from Laa, Cook and Lee, 2020, Figure 9.)}
\label{fig:pollen}
\end{figure}

@@

\begin{figure*}
   \centering
         \includegraphics[width=0.9\textwidth]{figures/liminal-stop-pause-refresh.png}
\caption{The clustering example from Figure \ref{fig:tsne-tour} using the liminal interface. Here a grand tour is displayed on the right hand side, with buttons allowing users to play, pause and refresh the tour animation. (Adapted from Lee, Laa and Cook, 2020, Figure 2.)}
\label{fig:tour-controls}
\end{figure*}

@@

\begin{figure}[htp]
\centerline{{\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp1.pdf}}
 {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp2.pdf}}
 {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp5.pdf}}}
\smallskip
\centerline{{\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp7.pdf}}
 {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp8.pdf}}
 {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp9.pdf}}}
\centerline{{\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp10.pdf}}
  {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp11.pdf}}
  {\includegraphics[width=0.32\textwidth]{figures/ggobi_book/prim7-pp13.pdf}}}
\caption{Stepwise identification of clusters in the physics data. Each time a cluster is clearely separated we stop the tour and brush the points, followed by another spin of the data, until we can capture the full distribution. (Adapted from Cook and Swayne, 2007, Figure 5.3.)}
\label{fig:prim7-tour}
\end{figure}

@@

\begin{figure*}
  \centering
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-orange.png}
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-green.png}
    \includegraphics[width=0.32\textwidth]{figures/svm-radial-purple.png}
  \caption{A grand tour run on the prediction boundaries of a radial support vector machine. (Left) The prediction region for points classified as orange produces a slice of a cube. (Middle) The predicition region for points classified as green produces another slice of the cube. (Right) The complete prediction region shows the points classified as purple are embedded within the green slice. (Adapted from Wickham, Hofmann and Cook, 2015, Figure 6.)}
  \label{fig:svm-tour}
\end{figure*}

@@

\begin{figure*}
   \centering
         \includegraphics[width=0.9\textwidth]{figures/scheidigger_nn_tour.png}
\caption{A grand tour run on the output of a deep neural network model for classification. The axes correspond to the probabilities that the model of an image belonging to a certain class. (Adapted from Li, Zhao and Scheidigger, 2020.)}
\label{fig:tour-nn}
\end{figure*}

@@

\begin{figure*}
  \centering
           \includegraphics[width=0.45\textwidth]{figures/allcenter-301.png}
         \includegraphics[width=0.45\textwidth]{figures/jetCluster-027.png}
\caption{Selected frames from using a grand tour of the physics data. Left: the three different types of measurements (shown in different colors) are aligned along different directions in parameter space. Right: an outlying point is marked with an asterisk symbol in the ATLAS7new facet. (Adapted from Cook, Laa and Valencia, 2018, Figures 6 and 7.)}
\label{fig:physics}
\end{figure*}

@@

\caption{Selected frames from using a grand tour of mouse retina single cell RNA-seq data with the radial transformation. The sage display was used to identify and verify cluster sepearation between the three highlighted clusters estimated from a clustering algorithm. (Adapted from Laa, Lee and Cook, 2020 Figure 6.)}
\label{fig:mouse-cluster}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.24\textwidth]{figures/torus-rings-4-with-torus-1.pdf}\includegraphics[width=0.24\textwidth]{figures/torus-rings-4-with-torus-2.pdf}
  \includegraphics[width=0.24\textwidth]{figures/torus-flat-6-1.pdf}\includegraphics[width=0.24\textwidth]{figures/torus-flat-6-2.pdf}
\caption{Several views of torii: (two at left) 4D ring torus, and (two at right) 6D flat torus. In each case, a subset has been highlighted which illustrate the low-dimensional donut shapes. (Adapted from Schloerke, et al., 2016, Figures 10 and 13.)}
\label{fig:geozoo}
\end{figure*}
